### 2017-10-31 Docs/Thesis/docs/chapter5.tex
more collectted data, update on some files

We perform

\begin{figure}[!ht]
	\centering
	\includegraphics[scale=0.75]{figures/ch5/iperfFlowsPs.pdf}
	\caption{the caption}
	\label{fig:iperfFlowsPs}
\end{figure}

\begin{figure}[!ht]
	\centering
	\includegraphics[scale=0.75]{figures/ch5/iperfFlowCdf.pdf}
	\caption{the caption}
	\label{fig:iperfFlowCdf}
\end{figure}

\begin{figure}[!ht]
	\centering
	\includegraphics[scale=0.75]{figures/ch5/iperfBandwidth.pdf}
	\caption{the caption}
	\label{fig:iperfBandwidth}
\end{figure}

\begin{figure}[!ht]
	\centering
	\includegraphics[scale=0.75]{figures/ch5/iperfWaveletMREA.pdf}
	\caption{the caption}
	\label{fig:iperfWaveletMREA}
\end{figure}

@@

@@

>>>>

\begin{figure}[t!]
	\centering
	\subfloat[\textit{skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/iperfFlowsPs.pdf}
		\label{fig:iperf-single-flowps}
	}
	\hspace{0mm}
	\subfloat[\textit{bigFlows-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/iperfBandwidth.pdf}
		\label{fig:iperf-single-bw}
	}
	\hspace{0mm}
	\subfloat[\textit{lan-diurnal-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/iperfFlowCdf.pdf}
		\label{fig:iperf-single-flowcdf}
	}
	\hspace{0mm}
	\subfloat[\textit{wan-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/iperfWaveletMREA.pdf}
		\label{fig:iperf-single-wavelet}
	}
	\caption{caption}
	\label{fig:iperf-single}
\end{figure}

@@

\begin{figure}[t!]
	\centering
	\subfloat[\textit{skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/iperftreeFlowsPs.pdf}
		\label{fig:iperf-flowps}
	}
	\hspace{0mm}
	\subfloat[\textit{bigFlows-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/iperftreeBandwidth.pdf}
		\label{fig:iperf-bw}
	}
	\hspace{0mm}
	\subfloat[\textit{lan-diurnal-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/iperftreeFlowCdf.pdf}
		\label{fig:iperf-flowcdf}
	}
	\hspace{0mm}
	\subfloat[\textit{wan-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/iperftreeWaveletMREA.pdf}
		\label{fig:iperf-tree-wavelet}
	}
	\caption{caption}
	\label{fig:iperf-tree}
\end{figure}

@@

\begin{figure}[t!]
	\centering
	\subfloat[\textit{skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/tinsFlowsPs.pdf}
		\label{fig:tins-single-flowps}
	}
	\hspace{0mm}
	\subfloat[\textit{bigFlows-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/tinsBandwidth.pdf}
		\label{fig:tins-single-bw}
	}
	\hspace{0mm}
	\subfloat[\textit{lan-diurnal-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/tinsFlowCdf.pdf}
		\label{fig:tins-single-flowcdf}
	}
	\hspace{0mm}
	\subfloat[\textit{wan-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/tinsWaveletMREA.pdf}
		\label{fig:tins-single-wavelet}
	}
	\caption{caption}
	\label{fig:tins-single}
\end{figure}
